%-------------------------
% Resume in Latex
% Author : Sooji Kim
% Website: https://github.com/skim1225/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/sooji-kim12/}{\Huge Sooji Kim}} & \faIcon{envelope} \href{mailto:kim.sooji1225@gmail.com}{kim.sooji1225@gmail.com}\\
  \href{https://www.linkedin.com/in/sooji-kim12/}{\faIcon{linkedin} sooji-kim12} & \faIcon{mobile-alt} 206-913-1847 & \href{https://github.com/skim1225}{\faIcon{github} skim1225}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Molecular Biology B.S. (In-major GPA: 3.62)}{Sept. 2018 -- June 2022}
      \resumeItemListStart
        \resumeItem{Programming Coursework}
          {Web Programming: 3.9, Genomic Informatics: 3.9, Intro Probability and Stats: 4.0, Computer Programming I: AP, Computer Programming I: AP}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------CERTIFICATES---------------
\section{Certificates}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coursera}{Online}
      {Advanced React, Django Web Framework, Version Control, Intro to Databases}{Dec. 2022 - Jan. 2023}
    \resumeSubheading
        {Free Code Camp}{Online}
        {Responsive Web Design}{Feb. 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Highland Pharmacy}{Edmonds, WA}
      {Pharmacy Assistant}{June 2018 - Present}
      \resumeItemListStart
        \resumeItem{Revamped pharmacy workflow}
          {Optimized the prescription filling workflow by increasing pharmacy assistant efficiency by restructuring generic and brand name drug inventory organization.}
        \resumeItem{Liaised between allied health professionals}
          {Seamlessly integrated patient care from refill request to medication pickup by answering phone calls and refilling prescriptions or liaising with prescribers' offices and insurance companies to fulfill patients' needs.}
        \resumeItem{Cost Savings}
            {Decreased pharmacy's costs and increased profit margins by monitoring drug price increases vs. insurance compensation daily and submitting price adjustment documents when necessary.}
      \resumeItemListEnd

    \resumeSubheading
      {COPE (Volunteer)}{Seattle, WA}
      {Health Scholar}{June 2019 - Aug. 2021}
      \resumeItemListStart
        \resumeItem{HCAHPS}
          {Improved Swedish Medical Center's HCAHPS survey results by advocating for patient care by answering call lights and promptly responding to patient requests or delegating issues to appropriate personnel.}
        \resumeItem{Mentorship}
          {Mentored junior health scholars by developing their confidence and knowledge in healthcare by answering questions and monitoring their duties.}
        \resumeItem{Cultural Competency}
          {Utilized Korean and Spanish language speaking skills to improve healthcare outcomes for non-English speaking patients by translating patients' needs to the patient care team.}
      \resumeItemListEnd

    \resumeSubheading
      {Seattle Music Partners (Volunteer)}{Seattle, WA}
      {Cello Mentor}{Sept. 2017 - Aug. 2018}
      \resumeItemListStart
        \resumeItem{Equity}
          {Expanded access to music education for students in low income and majority non-white schools by developing personalized music curriculum and providing private lessons which include music theory and performance.}
        \resumeItem{Mentorship}
          {Mentored young musicians by leading group discussions about equity and anti-racism and worked on developing work ethic and grit through practice.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{API}
      {REST API project with server-side code, client-side data fetching using JSON data,}
    \resumeSubItem{Buzzfeed Quiz Clone}
      {A buzzfeed style quix built using Typescript and Node.js mini back-end.}
    \resumeSubItem{Physics Based Action Game}
      {Leverages Javascript, CSS3, and HTML canvas to animate game sprites, implement collision detection, and program enemy AI.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, Python, Javascript, SQL}
     \hfill
     \textbf{Technologies}{:  React, Bootstrap, REST API, npm, Flask}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
